19Q2

### 2019-10-14 19Q2.Rmd
fixed CRISPR fusions and protein drug annots, moved prot to giant_files

```{r merge_crispr_fus, eval=FALSE}
fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
crispr_fus$Drug <- "CRISPR"
crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
crispr_fus$G2P_Drug_FusionPair <- "No"
crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
crispr_fus$Database <- "CRISPR"

@@

crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
crispr_prot <- merge(crispr_melt, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
crispr_prot <- select(crispr_prot, -Protein_Change)
crispr_prot$Drug <- "CRISPR"
crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
crispr_prot$G2P_Drug_Gene_Protein_Change <- "No"
crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
crispr_prot$G2P_Drug_Gene_Protein_Change_Lineage <- "No"
crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
crispr_prot$Database <- "CRISPR"

@@

**10/9 ENDED HERE**

```{r prot_wilcoxon_tests, eval=FALSE}
# crispr_prot <- unfactorize(crispr_prot)
# crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
# 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
# crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")

>>>>

```{r merge_crispr_fus, eval=FALSE}
fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
crispr_fus$Drug <- crispr_fus$Drug_Gene
crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
crispr_fus$G2P_Drug_FusionPair <- "No"
crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
crispr_fus$Database <- "CRISPR"

@@

crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
crispr_prot <- merge(crispr_melt, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
crispr_prot <- select(crispr_prot, -Protein_Change)
crispr_prot$Drug <- paste0("CRISPR_", crispr_prot$Gene)
crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
crispr_prot$G2P_Drug_Gene_Protein_Change <- "No"
crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
crispr_prot$G2P_Drug_Gene_Protein_Change_Lineage <- "No"
crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
crispr_prot$Database <- "CRISPR"

@@

**10/9 ENDED HERE**
**10/14 ENDED HERE**

Testing:
```{r}
dataframe <- crispr_prot
grouping <- c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")

count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
signif <- adj_signif(signif, alpha = 0.05)
signif <- signif[order(signif$p),]
signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
```

```{r prot_wilcoxon_tests, eval=FALSE}
# crispr_prot <- unfactorize(crispr_prot)
crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
# 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
# crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
